---
title: "Figures for FrEDI NPD Paper"
author: "CH, EM"
use:    "Contains figures for FrEDI NPD paper"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmarkdown::html_document:
    theme: spacelab
    toc: true
    toc_float: true
    toc_depth: 4
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  cache=F,
  warning = FALSE, 
  message = FALSE
  )
```

#Set-Up

### Load Packages

Load packages

```{r load_packages, echo = FALSE, include = FALSE}
require(tidyverse)
require(arrow)
require(xts)
require(dygraphs)
require(maps)
require(viridis)
require(rgeos)
require(maptools)
require(tidytext)
require(scales)
require(patchwork)
require(paletteer)
require(readxl)
```

### Paths

Set paths to files

```{r set_paths, include = FALSE}
###### Set code paths ######
### Path to main folder
#npdPath        <- ".." %>% file.path("../GitHub/FrEDI_NPD"); npdPath %>% list.files #CH path
npdPath        <- ".." %>% file.path("../"); npdPath %>% list.files    #EEM path


###### For data outputs ######
#stats_outPath    <- damagePath %>% file.path("output_stats")

### Temperature input file path
inputPath        <- npdPath %>% file.path("data", "input_files")

### Current analysis folder path
analysisPath     <- npdPath %>% file.path("analysis", "graphics_for_paper")

### Current path for where aggregate fredi dataframes are stored ###
frediDataPath  <- npdPath %>% file.path("output", "damages","fredi_analysis")
frediSVPath  <- npdPath %>% file.path("output", "damages","FrEDI_sv")


```


### Global Variables


```{r c_eraYears, include = FALSE, echo = FALSE}
c_eraYears  <- c(2050,2070,2090)

colors_full = c("#EA7580FF", "#F6A1A5FF", "#F8CD9CFF", "#86b98e", 
                "#4d8055", "#1BB6AFFF", "#088BBEFF","#172869FF")
#secondary_light, error-base, accent-warm-light, green-light, (green-dark), aqua-light, blue-dark
colors_6 = c("#f2938c", "#d54309", "#ffbc78", "#4d8055", "#97d4ea",
             "#1a4480")
colors_7 = c("#f2938c", "#d54309", "#ffbc78", "#86b98e","#4d8055",
             "#97d4ea","#1a4480")
colors_blues = c("#d9e8f6","#aacdec","#73b3e7","#005ea2","#0050d8",
                 "#1a4480","#162e51")


#define sector categories
labor_cat          <- c("Labor")
ag_cat             <- c("CIL Agriculture")
elect_cat          <- c("Electricity Demand and Supply", 
                    "Electricity Transmission and Distribution")
cil_health_cat     <- c("Air Quality","Valley Fever",
                    "CIL Extreme Temperature","Wildfire",
                    "Southwest Dust", "CIL Crime")
ats_health_cat     <- c("Air Quality","Valley Fever",
                    "ATS Extreme Temperature","Wildfire",
                    "Southwest Dust","CIL Crime")
infrastructure_cat <- c("Rail","Roads","Urban Drainage","Coastal Properties", 
                        "High Tide Flooding and Traffic", "Inland Flooding",
                        "Wind Damage")
eco_cat            <- c("Marine Fisheries", "Winter Recreation", "Water Quality")

#Dollar conversion from 2015 to 2020 USD (from BEA)
pricelevel_2015_to_2020 = 113.784/104.691

```


# Load the Data

```{r load_analysis_data, echo=FALSE}

#these files are created by the 4_fredi_analysis.R script

# All years, all trials, national annual impacts
df_fraw_nat1 <- read_parquet(frediDataPath %>%
                            file.path("baseline_impacts_nat_thru2050_constrained.parquet"))
df_fraw_nat2 <- read_parquet(frediDataPath %>%
                            file.path("baseline_impacts_nat_2050-2100_constrained.parquet"))
#bind years together
df_fraw_allnat <- rbind(df_fraw_nat1, df_fraw_nat2)
remove(df_fraw_nat1); remove(df_fraw_nat2)

# All years, national annual impact stats
df_fstat1  <- read_parquet(frediDataPath %>%
                          file.path("baseline_impacts_nat_thru2050_stats_constrained.parquet"))
df_fstat2  <- read_parquet(frediDataPath %>%
                          file.path("baseline_impacts_nat_2050-2100_stats_constrained.parquet"))
df_fstat3  <- read_parquet(frediDataPath %>%
                          file.path("baseline_impacts_nat_2100-2150_stats_constrained.parquet"))
df_fstat4  <- read_parquet(frediDataPath %>%
                          file.path("baseline_impacts_nat_2150-2200_stats_constrained.parquet"))
df_fstat5  <- read_parquet(frediDataPath %>%
                          file.path("baseline_impacts_nat_2200-2250_stats_constrained.parquet"))
df_fstat6  <- read_parquet(frediDataPath %>%
                          file.path("baseline_impacts_nat_2250-2300_stats_constrained.parquet"))

df_fstat <- rbind(df_fstat1, df_fstat2, df_fstat3, df_fstat4,df_fstat5,df_fstat6)
remove(df_fstat1); remove(df_fstat2); remove(df_fstat3); remove(df_fstat4); remove(df_fstat5);remove(df_fstat6)

# 2090, all trials, regional annual impacts
df_fraw_2090reg <- read_parquet(frediDataPath %>%
                            file.path("impacts_reg_2090_constrained.parquet"))

# 2090, regional annual impact stats
df_fstat_2090reg  <- read_parquet(frediDataPath %>% 
                            file.path("impacts_reg_2090_stats_constrained.parquet"))

# 2090, all trials, annual impacts for sectors with adaptation
df_fraw_2090adapt <- read_parquet(frediDataPath %>%
                            file.path("impacts_adapt_2090_constrained.parquet"))

# 2090, annual impact stats for sectors with adaptation
df_fstat_2090adapt <- read_parquet(frediDataPath %>%
                            file.path("impacts_adapt_2090_stats_constrained.parquet"))

# 2090, all trials, sectors with physical impacts
df_fraw_phys2090nat <- read_parquet(frediDataPath %>%
                            file.path("phys_impacts_nat_2090.parquet"))

# 2090, physical impact stats for sectors with physical impacts
df_fstat_2090phys<- read_parquet(frediDataPath %>% 
                            file.path("phys_impacts_nat_2090_stats.parquet"))

# load pre-processed files instead
damage_share_data <- read_parquet(file.path(frediDataPath,
              "Damage_GDP_Share_2100_constrained.parquet"))

npd_data <- read_parquet(file.path(frediDataPath,
              "npd_by_trial_constrained.parquet"))

# load pre-processed SV data
aq_sv <- read_excel(file.path(frediSVPath,"FrEDI_SV_Outputs_Air Quality - Premature Mortality.xlsx"), sheet = "FrEDI Outputs 1")

labor_sv <- read_excel(file.path(frediSVPath,"FrEDI_SV_Outputs_Labor.xlsx"), sheet = "FrEDI Outputs 1")


```


### Total Sector Summary 

(also Fig A2-1)

Sectoral Annual Damages in Billions 2020$
```{r table_allsectors_2090,echo=FALSE}

#Baseline Results
#used for main text #s and Table A2

print(df_fstat %>%
  filter(year ==2090) %>%
    mutate(mean = mean/1e9 * pricelevel_2015_to_2020) %>% #in billions
    mutate(X025 = X025/1e9 * pricelevel_2015_to_2020) %>%
    mutate(X50 = X50/1e9 * pricelevel_2015_to_2020) %>%
    mutate(X975 = X975/1e9 * pricelevel_2015_to_2020) %>%
    select(sector,X025,X50,X975,mean,year) %>%
    group_by(mean)%>%
    arrange(.by_group = TRUE) %>% mutate(across(c('X025','X50', 'X975'), ~ signif(.,2))))
  

#total summary
print (signif(df_fstat %>% 
        filter(year == 2090) %>%
        mutate(mean = mean * pricelevel_2015_to_2020/1e12) %>%
        mutate(X025 = X025 * pricelevel_2015_to_2020/1e12) %>%
        mutate(X50 = X50 * pricelevel_2015_to_2020/1e12) %>%
        mutate(X975 = X975 * pricelevel_2015_to_2020/1e12) %>%
        summarize_at(.vars = c("mean","X025","X50","X975"),sum,na.rm=T), 2))

```

# Tables

## Table 1
```{r table1,echo=FALSE,include=TRUE}

#Table 1
table1 <- df_fraw_allnat %>%
  filter(year==2090) %>%
  mutate(category = case_when(
    sector %in% labor_cat ~ "Labor (1)",
    sector %in% ag_cat ~ "Agriculture (1)",
    sector %in% elect_cat ~ "Electricity (2)",
    sector %in% ats_health_cat ~ "Health (6)",
    sector %in% infrastructure_cat ~ "Infrastructure (7)",
    sector %in% eco_cat ~ "Ecosystems+ Recreation (3)",
    TRUE ~ NA_character_)) %>% 
  filter(category != "NA") %>% 
  mutate(value=annual_impacts/1e9*pricelevel_2015_to_2020) %>% #billions 
  group_by_at(.vars = c('category','trial','year')) %>%
  summarize_at(c("value"), sum, na.rm=T) %>%#sum across categories per trial
  ungroup %>%
  group_by_at(.vars=c('category','year'))%>% #stats across trials
  summarize(X025=quantile(value,probs=0.025), 
            X50=quantile(value, probs=0.50),
            X975=quantile(value,probs=0.975),
            mean=mean(value)) %>% 
  ungroup %>%
  select('category','X025','X975','mean','year') 

table1 <- table1 %>% mutate(across(c('X025', 'X975', 'mean'), ~ signif(.,2)))

print(table1)

#total summary
print(signif(table1 %>%
        summarize_at(.vars = c("mean","X025","X975"),sum,na.rm=T), 2))

```

## Table 2 - physical impacts

```{r table2,echo=FALSE}

#Table 2
print(df_fstat_2090phys %>%
        select('sector','physicalmeasure','X025','X975','mean',
                'year','damageType')) %>%  #not in dollars so no conversions
  mutate(across(c('X025', 'X975', 'mean'), ~ signif(.,2)))

```

##Table 3
created elsewhere: code/ssp_sensitivity_runs/


## Appendix Table - A3-1
Adaptation
``` {r adapt_table,eval=TRUE, include=FALSE,echo=FALSE}

df_adapt_sectors <- df_fstat_2090adapt %>%
  mutate(X025 = X025 * pricelevel_2015_to_2020/1e9) %>% #2020 billions
  mutate(X975 = X975 * pricelevel_2015_to_2020/1e9) %>% #2020 billions
  mutate(mean = mean * pricelevel_2015_to_2020/1e9) %>%  #2020 billions
  select(sector,variant,X025,X975,mean,year,damageType)
  
  print(df_adapt_sectors %>% 
           mutate(across(c('X025', 'X975', 'mean'), ~ signif(.,2))))

```


# Figures

## Figure 2. Annual Impacts in Select Years

### Option A - without error bars

```{r Fig02_A,echo=FALSE}
##Annual Impacts for Baseline##

#filter relevant data for three years of interest and assign category to each sector

plots_stackedBar_bySector <- df_fstat %>%
  filter(year %in% c_eraYears) %>% mutate(year = as.factor(year)) %>%
  mutate(category = case_when(
    sector %in% labor_cat ~ "Labor (1)",
    sector %in% ag_cat ~ "Agriculture (1)",
    sector %in% elect_cat ~ "Electricity (2)",
    sector %in% ats_health_cat ~ "Health (6)",
    sector %in% infrastructure_cat ~ "Infrastructure (7)",
    sector %in% eco_cat ~ "Ecosystems+ Recreation (3)",
    TRUE ~ NA_character_)) %>% 
  filter(category != "NA") %>% 
  #filter(damageType == "Baseline") %>% 
  mutate(value = mean / 1e12 * pricelevel_2015_to_2020) #%>% trillions

#TO REORDER FROM LARGEST TO SMALLEST CATEGORY
cat_i <- plots_stackedBar_bySector %>% 
  group_by_at(.vars=c("category")) %>% 
  summarize_at(.vars=c("value"),sum,na.rm=T) %>%
  ungroup %>% arrange_at(.vars=c("value", "category"))
plots_stackedBar_bySector <- plots_stackedBar_bySector %>% 
  mutate(category = category %>% factor(levels = (cat_i$category))) %>%
  arrange_at(.vars=c("category"))
  #or mutate(category = category %>% factor(levels = rev(cat_i$category))) to plot smallest to largest



df_1 <- plots_stackedBar_bySector %>%
      ggplot() +
      geom_bar(aes(fill=category,y=value,x=year), 
               position="stack", 
               stat="identity",
               alpha = 0.7) +
      scale_y_continuous("Damages (Trillions)")+#,limits=c(0,3)) +
      scale_x_discrete("Year") + 
      #scale_fill_paletteer_d("LaCroixColoR::Pamplemousse",6,direction = 1)+
      scale_fill_manual(values=colors_6)+
      theme_minimal() +
      theme(axis.text = element_text(size=11), 
            axis.title = element_text(size =14),
            axis.title.y = element_text(margin = 
                                        margin(t = 0, r = 10, b = 0, l = 0)),
            axis.title.x = element_text(margin = 
                                        margin(t = 5, r = 0, b = 0, l = 0)),
            legend.text=element_text(size=10),
            legend.title=element_text(size=10, face="bold"),
            plot.title = element_text(size = 16, face = "bold"),
            plot.title.position = "plot")+
      labs(title="Annual U.S. Climate-Driven Damages", 
           subtitle="Mean Damages by Year and Category (Trillions $)",
           fill = "Sector Categories \n(number of sectors in category)")#,
           #caption = 'Figure 2. Mean climate-driven damages for the years 
           #2050, 2070, and 2090, colored by sector category' )+

df_1
ggsave(plot = df_1, filename = 'fig02.tiff',width = 5,height = 4)

print(df_1$data %>% filter(year == 2090) %>%
        #group_by_at("damageType") %>%
        summarize_at(.vars = c("value"),sum,na.rm=T) %>% 
         mutate(across(c('value'), ~ signif(.,2))))
print(df_1$data %>% filter(year == 2090) %>%
        group_by_at(c("sector")) %>%
        summarize_at(.vars = c("value"),sum,na.rm=T) %>% 
        mutate(across(c('value'), ~ signif(.,2))))
```

### Option B - with error bars
```{r Fig02_B, eval = FALSE,echo=FALSE}
##Baseline Case ##

 #same plot as option A, with error bars overlayed
 df_plotsum <- plots_stackedBar_bySector %>%
   group_by_at(c("year")) %>%
   summarize_at(.vars=c("mean","X025",'X975','X50'),sum,na.rm=T) %>%
   mutate(ymin = X025 / 1e12 *pricelevel_2015_to_2020) %>%
   mutate(ymax = X975 / 1e12 *pricelevel_2015_to_2020) %>%
   ungroup
 
df_1 <- plots_stackedBar_bySector %>%
       ggplot() +
       geom_bar(aes(fill=category,y=value,x=year),
                position="stack", 
                stat="identity", 
                alpha = 0.7) +
       scale_y_continuous("Damages (Trillions)",limits=c(0,12.5)) +
       scale_x_discrete("Year") +
       theme_minimal() +
       scale_fill_manual(values=colors_6)+
       theme(axis.text = element_text(size=11), 
             axis.title = element_text(size =14),
             axis.title.y = element_text(margin = 
                                        margin(t = 0, r = 10, b = 0, l = 0)),
             axis.title.x = element_text(margin = 
                                        margin(t = 5, r = 0, b = 0, l = 0)),
             legend.text=element_text(size=10),
             legend.title=element_text(size=10, face="bold"),
             plot.title = element_text(size = 16, face = "bold"),
             plot.title.position = "plot")+
       labs(title="Annual U.S. Climate-Driven Damages",
            subtitle="Mean Damages by Year and Cateogry (Trillions $)",
            fill = "Sector Categories \n(number of sectors in category)")+#,
            #caption = "Figure 2.")+
       geom_errorbar(data = df_plotsum, 
                     aes(x=year,ymin = ymin, ymax=ymax),
                     color = 'dark gray',
                     width = 0.25,
                     size=1)
 df_1
 ggsave(plot = df_1, filename = 'fig02_uncertainty.tiff',width = 5,height = 4)
 
 
#show in billions of 2020 USD
print(plots_stackedBar_bySector %>%
        filter(year==2090) %>%
        mutate(X025 = X025 / 1e9 *pricelevel_2015_to_2020) %>%
        mutate(X975 = X975 / 1e9 *pricelevel_2015_to_2020) %>%
        mutate(value = value *1e3) %>%
        group_by_at(c("category")) %>%
        summarize_at(.vars = c("value",'X025','X975'),sum,na.rm=T) %>% 
        mutate(across(c('value', 'X025','X975'), ~ signif(.,2))))
         
```
## Figure 3 Damages v GDP

```{r Figure3, fig.height=6, fig.width=9, echo=FALSE}


data <- damage_share_data %>%
  rename(value = "damages.baseline.pct") %>%
  group_by(year) %>%
  summarise(mean = mean(value),
              med  = median(value),
              #min  = min(value),
              max  = max(value),
              q01  = quantile(value,.01),
              #q025 = quantile(value,.025),
              q05  = quantile(value,.05),
              #q25  = quantile(value,.25),
              #q75  = quantile(value,.75),
              q95  = quantile(value,.95),
              #q975 = quantile(value,.975),
              q99  = quantile(value,.99), 
              .groups = 'keep')


## plot
data %>% 
  ggplot() +
  geom_line(aes(x=year, y=mean), 
            size=1) +
  geom_line(aes(x=year, y=med), 
            linetype='dashed', 
            size=1) +
  geom_ribbon(aes(x=year, ymin=q01, ymax=q99), 
              alpha=0.2, 
              color=NA) +
  geom_ribbon(aes(x=year, ymin=q05, ymax=q95), 
              alpha=0.1, 
              color=NA) +
  scale_x_continuous(breaks = c(2020,2050,2070,2100), 
                     limits = c(2020,2100),
                     labels = c(2020, 2050, 2070, 2100)) +
  scale_y_continuous(breaks = pretty_breaks(n = 8),
                     labels = scales::percent) +
  annotation_custom(
    grob = grid::rectGrob(gp = grid::gpar(col = NA, fill = "white")),
    xmin = 2100
    ) +
  scale_color_manual(values = colors) +
  scale_fill_manual(values  = colors) +
  scale_linetype_manual(values=c('dashed', 'solid', 'dotted')) +
  labs(x        = 'Year', 
       y        = expression(paste('Total Damage Share (% of US GDP)')),
       caption  = '',
       color    = '',
       fill     = '',
       alpha    = '',
       linetype = '') +
  theme_minimal() +
  theme(legend.position  = 'bottom',
        legend.title     = element_text(size=16, color='grey20'),
        legend.text      = element_text(size=16, color='grey20'),
        legend.key.size  = unit(0.75, 'cm'),
        legend.margin    = margin(0, 0, 0, 0),
        axis.title       = element_text(size=16),
        axis.text        = element_text(size=14),
        axis.line.x      = element_line(color = "black"),
        axis.ticks.x     = element_line(color = "black", size=1),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_line(color='grey70', linetype="dotted"),
        panel.grid.minor = element_blank(),
        plot.caption     = element_text(size=11, hjust=0.5),
        plot.title       = element_text(size=14, hjust=0.5),
        text             = element_text(family="sans-serif", color='grey20'))  +
  guides(color = guide_legend(reverse=T),
         fill  = guide_legend(reverse=T),
         alpha = guide_legend(reverse=T),
         linetype = guide_legend(reverse=T))

## export 
ggsave(filename = 'fig03.tiff', width = 9, height = 6, bg = 'white')

df <- data %>% 
  filter(year %in% c(2090, 2100, 2300))
print(df %>%  
        mutate(across(c('mean', 'med', 'max', 'q01', 'q05', 'q95', 'q99'), ~ signif(.,2))))
```



## Figure 4. Total Damages (statistics) by sector in 2090 

** Need to stitch 3 figures together in PowerPoint **

```{r Fig04_prep,fig.width=7,fig.height = 8,eval=TRUE,echo=FALSE}

# format the data into categories and re-order

plot_list <- list()

plots_basicBoxWhisker <- df_fraw_allnat %>%
  filter(year ==2090) %>%
  mutate(category = case_when(
    sector %in% labor_cat ~ "Labor (1)",
    sector %in% ag_cat ~ "Agriculture (1)",
    sector %in% elect_cat ~ "Electricity (2)",
    sector %in% ats_health_cat ~ "Health (6)",
    sector %in% infrastructure_cat ~ "Infrastructure (7)",
    sector %in% eco_cat ~ "Ecosystems+ Recreation (3)",
    TRUE ~ NA_character_)) %>% 
    mutate(value = annual_impacts / 1e9 * pricelevel_2015_to_2020) %>% #billions
  filter(category != "NA") 

#find order of sectors and categories, largest to smallest, then sort
sectors_i <- plots_basicBoxWhisker %>% 
        group_by_at(.vars=c("sector")) %>% 
        summarize_at(.vars=c("value"),mean,na.rm=T) %>%
        ungroup %>% arrange_at(.vars=c("value", "sector")) %>%
        arrange(desc(row_number())) #reverse order sectors

cat_i <- plots_basicBoxWhisker %>% 
        group_by_at(.vars=c("category")) %>% 
        summarize_at(.vars=c("value"),sum,na.rm=T) %>%
        ungroup %>% arrange_at(.vars=c("value", "category"))

plots_basicBoxWhisker <- plots_basicBoxWhisker %>% 
        mutate(sector = sector %>% 
                        factor(levels = sectors_i$sector)) %>%
        arrange_at(.vars=c("sector"))

plots_basicBoxWhisker <- plots_basicBoxWhisker %>% 
        mutate(category = category %>% 
                          factor(levels = rev(cat_i$category))) %>%
        arrange_at(.vars=c("category"))


# stats <- plots_basicBoxWhisker %>%
#   group_by(sector) %>%
#   mutate(X025=quantile(value,probs=0.025),
#               X25=quantile(value,probs=0.25), 
#               X50=quantile(value, probs=0.50),
#               X75=quantile(value,probs=0.75),
#               X975=quantile(value,probs=0.975),
#               mean=mean(value)) %>% ungroup

```

```{r boxplot_vals_function, echo=FALSE, include=FALSE}
#define function that calculates box plot values
BoxMedianQuant <- function(x) {
  v <- c(quantile(x, 0.025), quantile(x, 0.25), median(x), 
         quantile(x, 0.75), quantile(x, 0.975))
  names(v) <- c("ymin", "lower", "middle", "upper", "ymax")
  v
}

outliers <- function(x) {
  if (length(x) > 5) {
  subset(x, x < quantile(x, 0.025) | quantile(x, 0.975) < x)
  } else {
    return(NA)
  }
}
```

Three-panel box and whisker plot
```{r, Fig04_Option1,fig.width=9,fig.height = 5,echo=FALSE}
  
units <- 'Billions'
  p <- plots_basicBoxWhisker %>%
    #filter for ATS only
    filter(sector %in% c('ATS Extreme Temperature') ) %>%
    mutate(sector = sapply(sector,function(x) gsub("ATS Extreme Temperature",
                                                   "Temperature Related Mortality",x))) %>%
    ggplot(aes(x=reorder(sector,value,mean,na.rm=TRUE),
               y=value,
               fill=category))+
    coord_flip()+
    stat_summary(fun.data=BoxMedianQuant, 
                 geom="boxplot",
                 width=0.7,
                 alpha=0.6)+
    #stat_summary(fun.y = outliers, 
    #             geom = "point",
    #             color = 'dark gray',
    #             size=1)+
    stat_summary(fun=mean,geom = "point",
                 shape=23,
                 color='black')+
    scale_y_continuous(sec.axis=dup_axis(),limits=c(0,10250),labels = scales::comma)+
    scale_fill_manual(values=rev(colors_6))+ 
    scale_x_discrete(labels = function(x) str_wrap(x, width = 25))+
    labs(x='',
         y=paste0('Damages (',units,')'),
         title= 'U.S. Annual Climate-Driven Damages in 2090',
         subtitle='by sector, colored by sector category')+
    theme_minimal()+
    theme(legend.position = "none",
          legend.key=element_blank(), #c(0.65,0.4)
          legend.background=element_blank(),
          axis.text = element_text(size=12), 
          axis.title = element_text(size =12),
          axis.title.x = element_text(margin = 
                                        margin(t = 5, r = 0, b = 0, l = 0)),
          plot.margin = margin(l=5))+ 
    guides(fill=guide_legend(title=''))
    knitr::opts_chunk$set(fig.width=6,fig.height = 5)
  plot_list[[1]] = p
  p
  
  p1 <- plots_basicBoxWhisker %>%
    #filter for next top sectors (selected by hand)
    filter(sector %in% c('Air Quality', 'High Tide Flooding and Traffic',
                          'Labor','Wildfire') ) %>%
    mutate(sector = sapply(sector, function(x) gsub(" and"," &",x))) %>%
    mutate(sector = sapply(sector,function(x) gsub("High Tide Flooding & Traffic",
                                                   "Transportation Impacts from High Tide Flooding",x))) %>%
    ggplot(aes(x=reorder(sector,value,mean,na.rm=T),
               y=value,
               fill=category))+
    coord_flip()+
    stat_summary(fun.data=BoxMedianQuant, 
                 geom="boxplot",
                 width=0.7,
                 alpha=0.6)+
    #stat_summary(fun.y = outliers, 
    #             geom = "point",
    #             color = 'dark gray',
    #             size=1)+
    stat_summary(fun=mean,geom = "point",
                 shape=23,
                 color='black')+
    scale_y_continuous(sec.axis=dup_axis(), limits = c(NA,1125))+
    scale_fill_manual(values=rev(colors_6))+
    scale_x_discrete(labels = function(x) str_wrap(x, width = 25))+
    labs(x='',
         y=paste0('Damages (',units,')'),
         title= 'Climate-Driven Damages in 2090',
         subtitle='by sector, colored by sector category')+
    theme_minimal()+
    theme(legend.position = "none",
          legend.key=element_blank(), #c(0.65,0.4)
          legend.background=element_blank(),
          axis.text = element_text(size=12), 
          axis.title = element_text(size =12),
          axis.title.x = element_text(margin = 
                                        margin(t = 5, r = 0, b = 0, l = 0)),
          plot.margin = margin(l=5))+ 
    guides(fill=guide_legend(title=''))
    knitr::opts_chunk$set(fig.width=6,fig.height = 5)
  plot_list[[1]] = p1
  p1

  
  p2 <- plots_basicBoxWhisker %>%
    #select remaining sectors
    filter(!sector %in% c('ATS Extreme Temperature','Air Quality', 
                          'High Tide Flooding and Traffic',
                          'Labor','Wildfire') ) %>%
    #rename sectors
    mutate(sector = sapply(sector, 
                           function(x) gsub("Distribution","Dist.",x))) %>%
    mutate(sector = sapply(sector, 
                           function(x) gsub("Transmission","Trans.",x))) %>%
    mutate(sector = sapply(sector, function(x) gsub(" and"," &",x))) %>%
    mutate(sector = sapply(sector, function(x) gsub("CIL","",x))) %>%
    mutate(sector = sapply(sector, function(x) gsub("Electricity","Elec.",x))) %>%
    ggplot(aes(x=reorder(sector,value,mean,na.rm=T),
               y=value,
               fill=category))+
    coord_flip()+
    stat_summary(fun.data=BoxMedianQuant, 
                 geom="boxplot",
                 width = 0.7,
                 alpha=0.6)+
    #stat_summary(fun.y = outliers, 
    #             geom = "point",
    #             color = 'dark gray',
    #             size=1)+
    stat_summary(fun=mean,geom = "point",
                 shape=23,
                 color='black')+
    scale_y_continuous(sec.axis=dup_axis(), limits = c(NA,100))+
    scale_x_discrete(labels = function(x) str_wrap(x, width = 25))+
    labs(x='', 
         y=paste0('Damages (',units,')'),
         title= 'U.S. Annual Climate-Driven Damages in 2090',
         subtitle='by sector, colored by sector category')+
    scale_fill_manual(values=rev(colors_6[-4]))+
    theme_minimal()+
    theme(legend.position = 'none',
          #legend.key=element_blank(), #c(0.65,0.4)
          legend.background=element_blank(),
          axis.text = element_text(size=12), 
          axis.title = element_text(size =12),
          axis.text.y = element_text(hjust=1),
          axis.title.x = element_text(margin = 
                                      margin(t = 5, r = 0, b = 0, l = 0)),
          plot.margin = margin(l=5))+ 
    guides(fill=guide_legend(title='Sector Category'))
  p2
  
  
  #Option B is commented out
    ggsave(plot = p, filename = 'Figure4a(2).tiff',width = 6.75,height = 1.65, bg = 'white')
    ggsave(plot = p1, filename = 'Figur4b(2).tiff',width = 7,height = 2.5,bg = 'white')
    #ggsave(plot = p2, filename = 'Figure3lgnd.tiff',width = 6.8,height = 3.5)
    ggsave(plot = p2, filename = 'Figure4c(2).tiff',width = 7,height = 4.75,bg = 'white')
    
    
```



## Figure 5. Total Damages Map

### Per capita
```{r Fig05,fig.height=5,fig.width=9,echo=FALSE}
#Plot average of regional impacts/regional population for each trial (e.g. per capita)


#summarize across impactType for each sector and region
df_sector_region_sum <- df_fraw_2090reg %>%
    mutate(annual_impacts = annual_impacts * pricelevel_2015_to_2020) %>%
  # calculate total impacts per capita for each region and trail
    mutate(impacts_percap = annual_impacts / reg_pop) %>%
    ungroup %>%
#  # calculate the mean of per capita impacts across all trials (by region)
    group_by_at(c("region","sector")) %>%
    summarize(
              X025=quantile(impacts_percap,probs=0.025), 
              X975=quantile(impacts_percap, probs=0.975),
              impacts_percap = mean(impacts_percap, na.rm=T)) %>%
    ungroup
    
#sum across all sectors for each region
df_region_sum <- df_sector_region_sum %>%
    group_by_at(c("region")) %>%
    summarize(impacts_percap = sum(impacts_percap, na.rm=T),
              X025=sum(X025, na.rm=T), 
              X975=sum(X975, na.rm=T)) %>%
    ungroup
  

#Create dataframe by state (to be filled with impacts below)
MainStates <- map_data('state')
#Readin NCA regions
NCA_regions <- read.csv(paste0(analysisPath,"/NCA_Regions.csv"))
#Create dataframe with NCA region outlines
state_map <- map("state", fill=T, plot =FALSE)
state_map_match <- data.frame(name = state_map$names) %>%
  separate(name, c("State","subregion"), 
           sep= ":", remove=FALSE) %>%
  left_join(NCA_regions %>% select(State,Region))
rownames(state_map_match) <- state_map_match$name
  
#convert map to spatial polygon, then join with mapping table
state_map <- map2SpatialPolygons(state_map, IDs=state_map$names)
state_map <- SpatialPolygonsDataFrame(state_map, state_map_match)

#remove non valid points in the state map
invisible(gIsValid(state_map))
state_map <- gBuffer(state_map, byid=TRUE, width = 0)
invisible(gIsValid(state_map))

#dissolve map by state? and fortify to dataframe
area_map <- unionSpatialPolygons(state_map, IDs = state_map$Region)
area_map <- fortify(area_map)
area_map$group <- gsub(".1", "", x= area_map$group, fixed = T)

df <- df_region_sum
state_impacts <- data.frame(
    region = unique(MainStates$region),
    impacts = 0)
  
#Northwest
state_impacts$impacts[state_impacts$region %in% 
                        c('washington','idaho', 'oregon')] <- 
    df$impacts_percap[df$region == 'Northwest']

#Southwest
state_impacts$impacts[state_impacts$region %in% 
                          c('california','nevada',
                            'utah','colorado','arizona','new mexico')] <-
    df$impacts_percap[df$region == 'Southwest']

#Northern Great Plains
state_impacts$impacts[state_impacts$region %in% 
                          c('montana','wyoming', 'north dakota',
                            'south dakota','nebraska')] <-
    df$impacts_percap[df$region == 'Northern Plains']

#Southern Great Plains
state_impacts$impacts[state_impacts$region %in% 
                          c('kansas','oklahoma', 'texas')] <-
    df$impacts_percap[df$region == 'Southern Plains']

#Midwest
state_impacts$impacts[state_impacts$region %in% 
                          c('minnesota','iowa',
                            'missouri','wisconsin','indiana',
                            'illinois','michigan','ohio')] <-
    df$impacts_percap[df$region == 'Midwest']

#Southeast
state_impacts$impacts[state_impacts$region %in% 
                          c('arkansas','mississippi',
                            'louisiana','alabama','georgia',
                            'florida','south carolina',
                            'tennessee','kentucky',
                            'north carolina','virginia')] <-
    df$impacts_percap[df$region == 'Southeast']

#Northeast
state_impacts$impacts[state_impacts$region %in% 
                          c('west virginia','district of columbia',
                            'delaware','maryland',
                            'pennsylvania','new jersey','connecticut',
                            'rhode island',
                            'new york','massachusetts','vermont',
                            'new hampshire','maine')] <-
    df$impacts_percap[df$region == 'Northeast']

# Use the dplyr package to merge the MainStates and annual_impacts dataframes
MergedStates <- inner_join(MainStates, state_impacts, by = "region")

#Plot Map w/region borders
p <- ggplot(data = MergedStates, 
              mapping=aes(x=long, y=lat, group=group,fill=factor(impacts)))+
    geom_polygon(color="white",
                 size=0.2) + 
    geom_polygon(data=area_map, 
                 aes(x=long,y=lat,group=group), 
                 fill=NA, size=1,color="black") + 
    #discrete color scale
    scale_fill_brewer(palette = 'Greys', 
                    guide = guide_legend(reverse=TRUE),
                    labels=function(x) sprintf("$%1.0f", as.double(x)))+
    theme_minimal()+  
    theme(legend.key.size = unit(1, 'cm'),
          legend.title = element_text(size=12),
          legend.text = element_text(size=10),
          legend.position = "right",
          legend.box.margin = margin(t = 1, l = 1),
          axis.ticks.x=element_blank(),
          axis.ticks.y=element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          panel.background = 
            element_rect(fill = "white",
                         colour = "white",
                         size = 0.5,
                         linetype = "solid"),
          panel.grid.major = 
            element_line(size = 0.5, 
                         linetype = 'solid',
                         colour = "white"),
          panel.grid.minor = 
            element_line(size = 0.5, 
                         linetype = 'solid',
                         colour = "white"))+
          labs(title= 
               paste0('2090 Regional Climate-Driven Damages Per Capita'),
               fill= "Damages per Capita",
               #subtitle='Mean Damages per capita damages in each NCA region',
               x='',
               y='')
  
  ggsave(plot = p, filename = 'fig05_map.tiff',width = 9,height = 5)
  p
  
  print(df_region_sum %>% 
          mutate(across(c('impacts_percap','X025', 'X975'), ~ signif(.,2))))
  print(df_sector_region_sum %>% 
            mutate(across(c('impacts_percap','X025', 'X975'), ~ signif(.,2))))
  
```

### Per capita Regional sector donut charts
```{r percap_category_piecharts, echo = FALSE, include=TRUE}
  #make regional donut charts, by category (per capita)
  #already in 2020 dollars

#controls opacity of colors
darkop <- 'B3'


#sector category and category color
plots_pie_region <- df_sector_region_sum %>% #already in 2020 $
  mutate(category = case_when(
    sector %in% labor_cat ~ "Labor (1)",
    sector %in% ag_cat ~ "Agriculture (1)",
    sector %in% elect_cat ~ "Electricity (2)",
    sector %in% ats_health_cat ~ "Health (6)",
    sector %in% infrastructure_cat ~ "Infrastructure (7)",
    sector %in% eco_cat ~ "Ecosystems+ Recreation (3)",
    TRUE ~ NA_character_)) %>% 
  mutate(color_f = case_when(
    sector %in% labor_cat ~ paste0(colors_6[4],darkop),
    sector %in% ag_cat ~ paste0(colors_6[2],darkop),
    sector %in% elect_cat ~ paste0(colors_6[3],darkop),
    sector %in% ats_health_cat ~ paste0(colors_6[6],darkop),
    sector %in% infrastructure_cat ~ paste0(colors_6[5],darkop),
    sector %in% eco_cat ~ paste0(colors_6[1],darkop),
    TRUE ~ NA_character_)) %>% 
  filter(category != "NA") %>% 
  filter(impacts_percap != 'NaN')%>%
  arrange_at(.vars=c("impacts_percap", "sector"))

regions = unique(plots_pie_region$region)
plist <-list()
count=0


#donut plots (loop through each region)
for (iregion in regions){
  count = count+1
  
  #format donut chart dataframe
  p_temp <- plots_pie_region %>%
    filter(region == iregion) %>%
    #sum across sectors
    group_by_at(.vars=c("sector","color_f")) %>% 
    summarize_at(.vars=c("impacts_percap"),sum,na.rm=T) %>%
    ungroup %>% 
    #reorder based on per capita impacts
    arrange_at(.vars=c("impacts_percap")) %>%
    filter(impacts_percap >=0) %>%
    arrange(desc(impacts_percap))%>%
    #set non-top 4 sectors to 'remaining' group
    mutate(RowNum = row_number(),
           sector = ifelse(RowNum <= 4, sector, 'Remaining')) %>%
    group_by(sector) %>%
    #sum across all new groups (top four sectors and remaining)
    summarise(impacts_percap = sum(impacts_percap)) %>%
    arrange(desc(impacts_percap))%>%
    mutate(sector = as.factor(sector)) %>%
    #set colors of each sector (need to define all that are in top 4)
    mutate(color_f = case_when(
    sector %in% c('ATS Extreme Temperature') ~ paste0(colors_7[7],darkop),
    sector %in% c('Air Quality') ~ paste0(colors_7[6],darkop),
    sector %in% c('Labor') ~ paste0(colors_7[5],darkop),
    sector %in% c('CIL Agriculture') ~ paste0(colors_7[4],darkop),
    sector %in% c('Rail') ~ paste0(colors_7[3],darkop),
    sector %in% c('High Tide Flooding and Traffic') ~
      paste0(colors_7[2],darkop),
    sector %in% c('Roads') ~ paste0(colors_7[1],darkop),
    sector %in% c('Wildfire') ~ paste0('#c05600',darkop),
    sector %in% c('Wind Damage') ~ paste0('#446443',darkop),
    sector %in% c('Southwest Dust') ~ paste0('#936f38',darkop),
    sector %in% c('Remaining') ~ paste0('#D3D3D3',darkop)))
  
  p_temp$fraction <- p_temp$impacts_percap/sum(p_temp$impacts_percap)
  # Compute the cumulative percentages (top of each rectangle)
  p_temp$ymax <- cumsum(p_temp$fraction)
  # Compute the bottom of each rectangle
  p_temp$ymin <- c(0, head(p_temp$ymax, n=-1))
  # Compute label position
  p_temp$labelPosition <- (p_temp$ymax + p_temp$ymin) / 2
  # Compute a good label
  p_temp$label <- paste0(format(round(100*p_temp$fraction, 0), 
                                nsmall = 0),'%')
  label2 = paste0(format(round(100*sum(p_temp$impacts_percap)/
                              sum(plots_pie_region$impacts_percap),1),
                         nsmall=1),'%')
  
  #plot donut chart data
  p <- ggplot(p_temp, aes(ymax = ymax, ymin = ymin,xmax = 4, xmin = 3, 
                          fill = reorder(sector,(impacts_percap)))) + 
    geom_rect() +
    geom_text(x=4.25, 
              aes(y=labelPosition,label=''),
              size=5) +
    coord_polar(theta = "y") +
    scale_fill_manual(values =rev(p_temp$color_f), 
                    #switch the guide lines if no legend needed
                    #guide = guide_legend(reverse=TRUE))+#
                    guide = "none")+
    theme_void()+
    xlim(c(2,4))+
    labs(fill = "Top 4 Sectors",title = paste(iregion,label2))
    
  #p
  plist[[count]] <-p
  ggsave(p,filename = paste0('Figure5_',iregion,'.tiff'),width = 5,height = 5)

}

plist

```
## Figure 6. SV Results
plot SV results - raw data created elsewhere
graphics_for_paper/FrEDI_SV.Rmd

```{r Fig06,fig.height=8,fig.width=12,echo=FALSE}

#four panel plot
#a) risks by sv groups - AQ
#b) rates by race - AQ
#c) risk by sv groups - labor
#d) rates by race - labor

#AQ
aq_risks <- aq_sv %>%
  filter(year==2090, grepl('sv_', svGroupType)) %>%
  group_by_at(c("svGroupType")) %>%
  summarize_at(.vars=c("national_highRiskPop_sv","national_highRiskPop_ref",
                       "impPop_sv","impPop_ref"),sum,na.rm=T) %>%
  mutate(risk_per = 
           ((national_highRiskPop_sv/national_highRiskPop_ref) / 
           (impPop_sv/impPop_ref)) -1) %>%
  ungroup %>%
  mutate(across('svGroupType', str_replace, 'sv_minority', 'BIPOC')) %>%
  mutate(across('svGroupType', str_replace, 'sv_lowIncome', 'Low Income')) %>%
  mutate(across('svGroupType', str_replace, 'sv_noHS', 'No High-School\nDiploma')) %>%
  mutate(across('svGroupType', str_replace, 'sv_plus65', 'Over age 65')) %>%
  replace(is.na(.),0)


aq_rates <- aq_sv %>%
  filter(year==2090, !grepl('sv_', svGroupType)) %>%
  group_by_at(c("svGroupType")) %>%
  summarize_at(.vars=c("aveRate_sv"),sum,na.rm=T) %>%
  mutate(rate_per = aveRate_sv*1e5) %>% #rates per 100K
  ungroup %>%
  mutate(across('svGroupType', str_replace, 'race_amInd', 'American Indian\nor Alaska Native')) %>%
  mutate(across('svGroupType', str_replace, 'race_asian', 'Asian')) %>%
  mutate(across('svGroupType', str_replace, 'race_black', 'Black or African\nAmerican')) %>%
  mutate(across('svGroupType', str_replace, 'race_hispanic', 'Hispanic\nor Latino')) %>%
  mutate(across('svGroupType', str_replace, 'race_multiRacial', 'Two or more\nraces')) %>%
  mutate(across('svGroupType', str_replace, 'race_otherRace', 'Other Race')) %>%
  mutate(across('svGroupType', str_replace, 'race_pacIsl', 'Pacific Islander')) %>%
  mutate(across('svGroupType', str_replace, 'race_white', 'White, non-\nHispanic')) %>%
  replace(is.na(.),0)


labor_risks <- labor_sv %>%
  filter(year==2090, grepl('sv_', svGroupType)) %>%
  group_by_at(c("svGroupType")) %>%
  summarize_at(.vars=c("national_highRiskPop_sv","national_highRiskPop_ref",
                       "impPop_sv","impPop_ref"),sum,na.rm=T) %>%
  mutate(risk_per = 
           ((national_highRiskPop_sv/national_highRiskPop_ref) / 
           (impPop_sv/impPop_ref)) -1) %>%
  mutate(across('svGroupType', str_replace, 'sv_minority', 'BIPOC')) %>%
  mutate(across('svGroupType', str_replace, 'sv_lowIncome', 'Low Income')) %>%
  mutate(across('svGroupType', str_replace, 'sv_noHS', 'No High-School\nDiploma')) %>%
  mutate(across('svGroupType', str_replace, 'sv_plus65', 'Over age 65')) %>%
  ungroup %>%
  replace(is.na(.),0)

labor_rates <- labor_sv %>%
  filter(year==2090, !grepl('sv_', svGroupType)) %>%
  group_by_at(c("svGroupType")) %>%
  summarize_at(.vars=c("aveRate_sv"),sum,na.rm=T) %>%
  mutate(rate_per = aveRate_sv) %>% #rates per 100K
  mutate(across('svGroupType', str_replace, 'race_amInd', 'American Indian\nor Alaska Native')) %>%
  mutate(across('svGroupType', str_replace, 'race_asian', 'Asian')) %>%
  mutate(across('svGroupType', str_replace, 'race_black', 'Black or African\nAmerican')) %>%
  mutate(across('svGroupType', str_replace, 'race_hispanic', 'Hispanic\nor Latino')) %>%
  mutate(across('svGroupType', str_replace, 'race_multiRacial', 'Two or more\nraces')) %>%
  mutate(across('svGroupType', str_replace, 'race_otherRace', 'Other Race')) %>%
  mutate(across('svGroupType', str_replace, 'race_pacIsl', 'Pacific Islander')) %>%
  mutate(across('svGroupType', str_replace, 'race_white', 'White, non-\nHispanic')) %>%
  ungroup %>%
  replace(is.na(.),0)


#make 4 panel plot of bar charts
### Iterate over sectors
#create plot for each sector
plot_1 <-  aq_risks %>% 
  mutate(risk_per = risk_per*100) %>%
  ggplot() +
  ### bar plot
  geom_bar(aes(x=reorder(svGroupType, risk_per), y=risk_per),
           stat="identity",
           fill=colors_7[6],
           width = 0.6) +
  theme_bw() +
  theme_minimal() +
  coord_flip()+
  ### Scales
  ggtitle("Air Quality:\nMean Difference in Risk Relative to the \nNational Population in 2090") +
  scale_y_continuous("Percent", 
                     limits = c(0,50),
                      breaks = seq(0, 100, by=10)) +
  scale_x_discrete("Socially-Vulnerable Groups") +
  scale_fill_manual(values=colors_6[1]) +
  geom_text(aes(x=reorder(svGroupType, risk_per), 
                y=risk_per,
                label=paste0(round(risk_per, 0),"%"), 
                vjust=0.5,
                hjust=-1),
            position = position_dodge(1),
            color    = 'grey20',
            size     = 4) +
  theme(
    panel.grid.minor = element_blank(),
    axis.text.x = element_text(size=10),
    axis.text.y = element_text(size = 10),
    axis.title.y = element_text(vjust=2.5)
  )


##plot2
plot_2 <-  aq_rates %>% 
  ggplot() +
  ### bar plot
  geom_bar(aes(x=reorder(svGroupType, rate_per), y=rate_per),
           stat="identity",
           fill=colors_7[7],
           width = 0.6) +
  theme_bw() +
  theme_minimal() +
  coord_flip()+
  ### Scales
  ggtitle("Air Quality:\nAdditional Mortality in 2090") +
  scale_y_continuous("Mortality Rate per 100,000", 
                     limits = c(0,25),
                      breaks = seq(0, 25, by=5)) +
  scale_x_discrete("Race & Ethnicity") +
  geom_text(aes(x=reorder(svGroupType, rate_per), 
                y=rate_per,
                label=paste0(round(rate_per, 0)), 
                vjust=0.5,
                hjust=-1),
            position = position_dodge(1),
            color    = 'grey20',
            size     = 4) +
  theme(
    panel.grid.minor = element_blank(),
    axis.text.x = element_text(size=10),
    axis.text.y = element_text(size = 10),
    axis.title.y = element_text(vjust=2.5)
  )

#plot_2


plot_3 <-  labor_risks %>% 
  mutate(risk_per = risk_per*100) %>%
  ggplot() +
  ### bar plot
  geom_bar(aes(x=reorder(svGroupType, risk_per), y=risk_per),
           stat="identity",
           fill=colors_7[6],
           width = 0.6) +
  theme_bw() +
  theme_minimal() +
  coord_flip()+
  ### Scales
  ggtitle("Labor:\nMean Difference in Risk Relative to the \nNational Population in 2090") +
  scale_y_continuous("Percent", 
                     limits = c(-10,40),
                      breaks = seq(-10, 100, by=10)) +
  scale_x_discrete("Socially-Vulnerable Groups") +
  geom_text(aes(x=reorder(svGroupType, risk_per), 
                y=risk_per,
                label=paste0(round(risk_per, 0),"%"), 
                vjust=0.5,
                hjust=-1),
            position = position_dodge(1),
            color    = 'grey20',
            size     = 4) +
  theme(
    panel.grid.minor = element_blank(),
    axis.text.x = element_text(size=10),
    axis.text.y = element_text(size = 10),
    axis.title.y = element_text(vjust=2.5)
  )

#plot_3

plot_4 <-  labor_rates %>% 
  ggplot() +
  ### bar plot
  geom_bar(aes(x=reorder(svGroupType, rate_per), y=rate_per),
           stat="identity",
           fill=colors_7[7],
           width = 0.6) +
  theme_bw() +
  theme_minimal() +
  coord_flip()+
  ### Scales
  ggtitle("Labor:\nAdditional Hours Lost Per Capita in 2090") +
  scale_y_continuous("Labor Hours Lost Per Capita", 
                     limits = c(0,80),
                      breaks = seq(0, 80, by=10)) +
  scale_x_discrete("Race & Ethnicity") +
  geom_text(aes(x=reorder(svGroupType, rate_per), 
                y=rate_per,
                label=paste0(round(rate_per, 0)), 
                vjust=0.5,
                hjust=-1),
            position = position_dodge(1),
            color    = 'grey20',
            size     = 4) +
  theme(
    panel.grid.minor = element_blank(),
    axis.text.x = element_text(size=10),
    axis.text.y = element_text(size = 10),
    axis.title.y = element_text(vjust=2.5)
  )

#plot_4

plot_i <- plot_1 + plot_3 + plot_2 +plot_4
plot_i <- plot_i + plot_layout(ncol = 2) + plot_layout(heights = c(1,2))#widths = c(1,2))
plot_i
#plot_i <- plot_1


#plot_i <- plot_i + 
          plot_annotation(title = "Annual Climate-Driven Impacts",
                          caption = "")
  
plot_i

ggsave(plot = plot_i, filename = 'fig06.tiff',width = 12,height = 8)
```


## Figure 7 - Discounting Method Box Plot

```{r Fig07, fig.height=5, fig.width=7, echo=FALSE}


data <- npd_data

##########################
######### by discount rate
##########################

## plot data specific to this plot
plot.data = data %>% 
  filter(discount.rate %in% 
           c('1.5% Ramsey', '2.0% Ramsey', '2.5% Ramsey', "3.0% Ramsey"), #2.0% CDR #Figure A6
           #c('1.5% Ramsey', '2.0% Ramsey', '2.5% Ramsey', "3.0% Ramsey"), #Figure 6
         emissions.year==2020) %>% 
  distinct() %>% 
  arrange(trial) %>% 
  ungroup()

## select grouping
group = c('emissions.year', 'gas', 'discount.rate')

## labels
plot.data %<>% group_by_at(group) %>%
  mutate(scghg.mean  = mean(scghg),
         scghg.lower = quantile(scghg,.025),
         scghg.upper = quantile(scghg,.975),
         scghg.75 = quantile(scghg,.75),
         label.position = mean(scghg)) %>%
  ungroup()


## ordering of central rate for alpha transparency
plot.data$discount.rate <- factor(plot.data$discount.rate, 
                                  levels=c("1.5% Ramsey", "2.0% Ramsey", 
                                           "2.5% Ramsey", "3.0% Ramsey"))

## ordering of damage functions
#plot.data$adaptation <- factor(plot.data$adaptation, 
#                               levels=c('Default Adaptation'))

## all three just the boxplot
## function to help with boxplots
quantiles_95 <- function(x) {
  r <- quantile(x, probs=c(.025, 0.25, 0.5, 0.75, 0.975))
  names(r) <- c("ymin", "lower", "middle", "upper", "ymax")
  r
}

## function for labels
means = plot.data %>% 
  group_by(discount.rate) %>% 
  summarise(means=mean(scghg)) %>% 
  mutate(across(c('means'), ~ signif(.,2))) 

p <- plot.data %>%
  ggplot() +
  stat_summary(aes(x=scghg, y=discount.rate, color=discount.rate,
                   fill=discount.rate),
               alpha    = 0.5,
               geom     = "boxplot",
               fun.data = quantiles_95, 
               width    = 0.5, 
               #position = position_dodge(.9),
               show.legend=T) + 
  stat_summary(aes(x=scghg, y=discount.rate, color=discount.rate),
               alpha = 1,
               fun   = mean, 
               geom  = "point", 
               shape = 8, 
               size  = 4, 
               #position = position_dodge(.9),
               show.legend=F) +
  geom_text(data=means, 
            aes(x=means, y=discount.rate, group=discount.rate, 
                label=paste0('$', round(means, 2)), vjust=-2),
            position = position_dodge(1.3),
            color    = 'grey20',
            size     = 4,
            family   = "sans-serif") +
  labs(
    # title = 'XXX')),
    x     = expression(paste('Dollars per ton of ', CO[2])),
    y     = '',
    color = 'Discount Rate',
    fill  = 'Discount Rate',
    alpha = 'Discount Rate') +
  scale_x_continuous(
  #  limits = c(0,110),
  #  # breaks = seq(0,5,1), 
    labels = scales::dollar)+#,
  #  expand = expansion(mult=c(0,0))) +
  scale_y_discrete(expand = expansion(mult=c(0.0,0))) +
  scale_color_manual(values = colors_6) +
  scale_fill_manual(values  = colors_6) +
  coord_cartesian(xlim = c(0,quantile(plot.data$scghg,0.99))) + #0.985
  theme_minimal() +
  theme(legend.position = c(0.75, 0.65),
        legend.title    = element_text(size=12),
        legend.text     = element_text(size=12),
        legend.key.size = unit(0.75, 'cm'),
        legend.margin   = margin(-10, 0, 0, 0),
        axis.title.x    = element_text(size=14,hjust=0.5,vjust=-0.5),
        axis.text       = element_text(size=12),
        #axis.text.x = element_text(scales::dollar),
        axis.text.y     = element_blank(),
        plot.caption    = element_text(size=11, hjust=0.5),
        #text           = element_text(family="sans-serif", color='grey20')) +
        text            = element_text( color='grey20')) +
  guides(color = guide_legend(reverse = T),
         fill  = guide_legend(reverse = T, 
                              override.aes = list(linetype = 0, alpha=0.7)),
         alpha = guide_legend(reverse = T))

p

ggsave(p, filename = 'fig07.tiff', width=7, height=3.5, bg = 'white')

```

## Appendix Figure A1-1.
RFF temperature, population, and gdp - created elsewhere
Process_RFF_Temp.Rmd


## Appendix Figure A2-1.  

Annual Damages Timeseries - all sectors (national total)

Plot annual impacts by sector (National Totals)

currently ordered by decreasing mean in 2090 - 

```{r annual_bySector,eval=TRUE,fig.height=12,fig.width=9,echo=FALSE}
 plots_annual_bySector <- df_fstat %>%
   #if plotting 2100 version
   #filter(year <= 2100) %>%
   #if plotting 2300 version
   filter(year <= 2100 & year > 2020) %>%
   mutate_at(.vars = c('X025','X50', 'mean','X975'), 
             function(x){x / 1e9 *pricelevel_2015_to_2020}) %>% # billions 2020$
   mutate(sector = sapply(sector, 
                          function(x) gsub("ATS Extreme Temperature","Temperature Related Mortality",x))) %>%
   mutate(sector = sapply(sector, 
                          function(x) gsub("High Tide Flooding and Traffic",
                                           "Transportation Impacts from High Tide Flooding",x))) %>%
   mutate(sector = sapply(sector, function(x) gsub("CIL","",x)))

#order sectors by decreasing mean in 2090  
sectors_i <- plots_annual_bySector %>% 
         filter(year ==2100) %>%
         group_by_at(.vars=c("sector")) %>% 
         summarize_at(.vars=c("mean"),sum,na.rm=T) %>%
         ungroup %>% arrange(desc(mean), sector) 

### Iterate over sectors
#create plot for each sector
plots_i <- 
  sectors_i$sector %>% lapply(function(sector_j){
      df_j  <- plots_annual_bySector %>% filter(sector == sector_j)
      ### Make plot 
      ### Plot
      plot_j  <- df_j %>% ggplot() +
      ### Ribbon plot
      geom_ribbon(aes(x=year, ymin = X025, ymax = X975),
                  alpha=0.2) +
      ### Mean Line
      geom_line(aes(x=year, y=mean), 
                linetype = 2, 
                alpha=0.8) +
      ### Median Line
      geom_line(aes(x=year, y=X50), 
                linetype = 1, 
                alpha=0.8) +
      ### Scales
      ggtitle(str_wrap(sector_j,20)) +
      scale_x_continuous("Year", 
                         breaks = seq(2000, 2100, by=25)) + #2300
                         #breaks = seq(2020,2100, by =20)) +
      scale_y_continuous("Billions",
                        #"Annual Impacts\n(Billions)",
                         labels=label_scientific(digits = 2)) + 
      scale_fill_discrete("Sector") + 

      ### Guides/Themes
      guides(fill=guide_legend(ncol=2,byrow=FALSE)) +
      theme_bw()+
      theme(legend.position = "none",
              axis.text.x = element_text(angle = 90, vjust = 0.5, 
                                         hjust=1, size = 8),
              axis.text.y = element_text(size = 8),
              plot.title  = element_text(size = 8, face = "bold"),
      strip.text  = element_text(size = 8),
      axis.title  = element_text(size = 9))
      ### Return
      return(plot_j)
    })


### Make total plot
df_j  <- plots_annual_bySector %>% 
        group_by(year) %>%
        summarize(mean = sum(mean, na.rm=T)/1e3,
                  X50=sum(X50, na.rm=T)/1e3,
                  X025=sum(X025, na.rm=T)/1e3, 
                  X975=sum(X975, na.rm=T)/1e3) %>%
        ungroup()
      
### Plot
plot_j  <- df_j %>% 
  ggplot() +
  ### Ribbon plot
  geom_ribbon(aes(x=year, ymin = X025, ymax = X975),
                alpha=0.2) +
  ### Mean Line
  geom_line(aes(x=year, y=mean), 
                linetype = 2, 
                alpha=0.8) +
   ### Median Line
  geom_line(aes(x=year, y=X50), 
                linetype = 1, 
                alpha=0.8) +
  ### Scales
  ggtitle(str_wrap('Total',20)) +
  scale_x_continuous("Year", 
                     breaks = seq(2000, 2100, by=25)) + 
  scale_y_continuous("Trillions",
                      labels=label_scientific(digits = 2)) + 
  scale_fill_discrete("Sector") + 

### Guides/Themes
  guides(fill=guide_legend(ncol=2,byrow=FALSE)) +
  theme_bw()+
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90, vjust = 0.5, 
                                  hjust=1, size = 8),
        axis.text.y = element_text(size = 8),
        plot.title  = element_text(size = 8, face = "bold"),
        strip.text  = element_text(size = 8),
        axis.title  = element_text(size = 9))

       
### Arrange plots
### Add plots together
num_plots = length(plots_i)+1
for(j in 1:num_plots){
  if(j == 1){ plot_i <- plots_i[[j]] 
  } else if(j ==num_plots) { plot_i <- plot_i + plot_j
  } else { plot_i <- plot_i + plots_i[[j]] 
  }
}
### Layout
plot_i <- plot_i + plot_layout(ncol = 3)
plot_i <- plot_i + 
          plot_annotation(title = "Annual Climate-Driven Impacts",
                          caption = "")
  
plot_i

ggsave(plot = plot_i, filename = 'fa2-1.tiff',width = 9,height = 12)

```



## Appendix Figure A2-2.  

### Map - total annual damages map
```{r Map_annual_total_damages,fig.height=5,fig.width=9,echo=FALSE}
#***************************************************************  
# map absolute damages

#summarize mean across trials
df_sector_region_sum <- df_fraw_2090reg %>%
    mutate(annual_impacts = annual_impacts /1e9 * pricelevel_2015_to_2020) %>%
    #calculate mean regional impacts across all sectors
    group_by_at(c("region","sector","year")) %>%
    summarize(value = mean(annual_impacts, na.rm=T)) %>%
    ungroup
    
#sum across all sectors for each region
df_region_sum <- df_sector_region_sum %>%
    group_by_at(c("region","year")) %>%
    summarize(annual_impacts = sum(value, na.rm=T)) %>%
    ungroup
  

#Create dataframe by state (to be filled with impacts below)
MainStates <- map_data('state')
#Read in NCA regions
NCA_regions <- read.csv(paste0(analysisPath,"/NCA_Regions.csv"))
#Create dataframe with NCA region outlines
state_map <- map("state", fill=T, plot =FALSE)
state_map_match <- data.frame(name = state_map$names) %>%
  separate(name, c("State","subregion"), sep= ":", remove=FALSE) %>%
  left_join(NCA_regions %>% select(State,Region))
rownames(state_map_match) <- state_map_match$name
  
#convert map to spatial polygon, then join with mapping table
state_map <- map2SpatialPolygons(state_map, IDs=state_map$names)
state_map <- SpatialPolygonsDataFrame(state_map, state_map_match)

#remove invalidities in the state map
invisible(gIsValid(state_map))
state_map <- gBuffer(state_map, byid=TRUE, width = 0)
invisible(gIsValid(state_map))

#dissolve map by state? and fortify to dataframe
area_map <- unionSpatialPolygons(state_map, IDs = state_map$Region)
area_map <- fortify(area_map)
area_map$group <- gsub(".1", "", x= area_map$group, fixed = T)

plot_list <- list()
plot_count <- 1

#Get impacts data for each state (and scenario)
df <- df_region_sum

state_impacts <- data.frame(
    region = unique(MainStates$region),
    impacts = 0)
  
#Northwest
state_impacts$impacts[state_impacts$region %in% c('washington','idaho',
                                                  'oregon')] <- 
    df$annual_impacts[df$region == 'Northwest']
#Southwest
state_impacts$impacts[state_impacts$region %in% 
                          c('california','nevada',
                            'utah','colorado','arizona','new mexico')] <-
    df$annual_impacts[df$region == 'Southwest']
#Northern Great Plains
state_impacts$impacts[state_impacts$region %in% 
                          c('montana','wyoming', 'north dakota',
                            'south dakota','nebraska')] <-
    df$annual_impacts[df$region == 'Northern Plains']
#Southern Great Plains
state_impacts$impacts[state_impacts$region %in% 
                          c('kansas','oklahoma', 'texas')] <-
    df$annual_impacts[df$region == 'Southern Plains']
#Midwest
state_impacts$impacts[state_impacts$region %in% 
                          c('minnesota','iowa',
                            'missouri','wisconsin','indiana',
                            'illinois','michigan','ohio')] <-
    df$annual_impacts[df$region == 'Midwest']
#Southeast
state_impacts$impacts[state_impacts$region %in% 
                          c('arkansas','mississippi',
                            'louisiana','alabama','georgia',
                            'florida','south carolina',
                            'tennessee','kentucky',
                            'north carolina','virginia')] <-
    df$annual_impacts[df$region == 'Southeast']
#Northeast
state_impacts$impacts[state_impacts$region %in% 
                          c('west virginia','district of columbia',
                            'delaware','maryland',
                            'pennsylvania','new jersey','connecticut',
                            'rhode island','new york','massachusetts',
                            'vermont','new hampshire','maine')] <-
    df$annual_impacts[df$region == 'Northeast']

# Use the dplyr package to merge the MainStates and annual_impacts dataframes
MergedStates <- inner_join(MainStates, state_impacts, by = "region")


#plot regional map data
p <- ggplot(data = MergedStates,
            mapping=aes(x=long, y=lat, group=group,fill=(factor(impacts))))+
    geom_polygon(color="white",size=0.2) + 
    geom_polygon(data=area_map, 
                 aes(x=long,y=lat,group=group), 
                 fill=NA, 
                 size=1,
                 color="black") + 
    scale_fill_brewer(palette = 'Greys', 
                    guide = guide_legend(reverse=TRUE),
                    labels=function(x) sprintf("$%1.0f", as.double(x)))+

    theme_minimal()+  
    theme(legend.key.size = unit(0.75, 'cm'),
          legend.title = element_text(size=12),
          legend.text = element_text(size=10),
          legend.position = "right",
          legend.box.margin = margin(t = 1, l = 1),
          axis.ticks.x=element_blank(),
          axis.ticks.y=element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          panel.background = 
            element_rect(fill = "white",
                         colour = "white",
                         size = 0.5, 
                         linetype = "solid"),
          panel.grid.major = 
            element_line(size = 0.5, 
                         linetype = 'solid',
                         colour = "white"),
          panel.grid.minor = 
            element_line(size = 0.5, 
                         linetype = 'solid',
                         colour = "white"))+
    labs(title= '2090 Climate-Driven Damages by Region',
         subtitle='Mean Damages from all Sectors',
         x='',
         y='',
         fill= 'Damages (Billions)')

  ggsave(plot = p, filename = 'fa2-2_map.tiff',width = 9,height = 5)
  p
  print(df_region_sum %>% 
          mutate(across(c('annual_impacts'), ~ signif(.,2))))
```

### Absolute Regional sector pie charts
```{r abs_category_piecharts, include=FALSE, echo = FALSE}
  #make regional donut charts, by category (absolute)
#already in 2020 dollars

#specifies opacity
darkop <- 'B3'


plots_pie_regionmarginal <- df_sector_region_sum %>%
  mutate(category = case_when(
    sector %in% labor_cat ~ "Labor (1)",
    sector %in% ag_cat ~ "Agriculture (1)",
    sector %in% elect_cat ~ "Electricity (2)",
    #sector %in% cil_health_cat ~ "Health (CIL) (6)",  
    sector %in% ats_health_cat ~ "Health (6)",
    sector %in% infrastructure_cat ~ "Infrastructure (7)",
    sector %in% eco_cat ~ "Ecosystems+ Recreation (3)",
    TRUE ~ NA_character_)) %>% 
  mutate(color_f = case_when(
    sector %in% labor_cat ~ paste0(colors_6[4],darkop),
    sector %in% ag_cat ~ paste0(colors_6[2],darkop),
    sector %in% elect_cat ~ paste0(colors_6[3],darkop),
    sector %in% ats_health_cat ~ paste0(colors_6[6],darkop),
    sector %in% infrastructure_cat ~ paste0(colors_6[5],darkop),
    sector %in% eco_cat ~ paste0(colors_6[1],darkop),
    TRUE ~ NA_character_)) %>% 
  filter(category != "NA") %>% 
  filter(value != 'NaN')%>%
  arrange_at(.vars=c("value", "sector"))


regions = unique(plots_pie_regionmarginal$region)
plist <-list()
count=0


#category pie charts
#for (iregion in regions){
#  count = count+1
#   p_temp <- plots_pie_regionmarginal %>%
#    filter(region == iregion) %>%
#    group_by_at(.vars=c("category","color_f")) %>% 
#   summarize_at(.vars=c("mean"),sum,na.rm=T) %>%
#   ungroup %>% arrange_at(.vars=c("mean", "category","color_f"))
#   #pie(p_temp$annual_impacts, labels='',col=p_temp$color_f)
#   p <- ggplot(p_temp, aes(x = "", y = mean, 
#                           fill = reorder(category,mean))) +
#   geom_col(color = "black") +
#   geom_text(aes(label = ''),
#             position = position_stack(vjust = 0.5)) +
#   coord_polar(theta = "y") +
#   scale_fill_manual(values =(p_temp$color_f), 
#                     guide = guide_legend(reverse=TRUE))+#,
#                     #labels=function(x) sprintf("$%1.0f", as.double(x))) +
#     theme_void()+
#     labs(fill = "Categories",title = iregion)
#   plist[[count]] <-p
#   ggsave(p,filename = paste0('Figure9a_',iregion,'.tiff'),width = 5,height = 5)
# }


#sector pie charts
# for (iregion in regions){
#   count = count+1
#   
#   p_temp <- plots_pie_regionmarginal %>%
#    filter(region == iregion) %>%
#    group_by_at(.vars=c("sector","color_f")) %>% 
#   summarize_at(.vars=c("mean"),sum,na.rm=T) %>%
#   ungroup %>% arrange_at(.vars=c("mean")) %>%
#   filter(mean >=0) %>%
#     arrange(desc(mean))%>%
#     mutate(RowNum = row_number(),
#            sector = ifelse(RowNum <= 4, sector, 'Remaining')) %>%
#     group_by(sector) %>%
#     summarise(mean = sum(mean)) %>%
#     arrange(desc(mean))%>%
#     mutate(sector = as.factor(sector)) %>%
#     mutate(color_f = case_when(
#     sector %in% c('ATS Extreme Temperature') ~ paste0(colors_7[7],darkop),
#     sector %in% c('Air Quality') ~ paste0(colors_7[6],darkop),
#     sector %in% c('Labor') ~ paste0(colors_7[5],darkop),
#     sector %in% c('CIL Agriculture') ~ paste0(colors_7[4],darkop),
#     sector %in% c('Rail') ~ paste0(colors_7[3],darkop),
#     sector %in% c('High Tide Flooding and Traffic') ~ paste0(colors_7[2],darkop),
#     sector %in% c('Roads') ~ paste0(colors_7[1],darkop),
#     sector %in% c('Wildfire') ~ paste0('#c05600',darkop),
#     sector %in% c('Wind Damage') ~ paste0('#446443',darkop),
#     sector %in% c('Southwest Dust') ~ paste0('#936f38',darkop),
#     sector %in% c('Remaining') ~ paste0('#D3D3D3',darkop)))
#   
#   #p_temp$sector <- factor(p_temp$sector)
#   
#   #pie(p_temp$annual_impacts, labels='',col=p_temp$color_f)
#   
#   p <- ggplot(p_temp, aes(x = "", y = mean, fill = reorder(sector,mean))) +
#   geom_col(color = "black") +
#   geom_text(aes(label = ''),
#             position = position_stack(vjust = 0.5)) +
#   coord_polar(theta = "y") +
#   scale_fill_manual(values =rev(p_temp$color_f), 
#                     guide = guide_legend(reverse=TRUE))+#,
#                     #labels=function(x) sprintf("$%1.0f", as.double(x))) +
#     theme_void()+
#     labs(fill = "Top 4 Sectors",title = iregion)
#   plist[[count]] <-p
# }

#plist


#donut plots
for (iregion in regions){
  count = count+1
  
  p_temp <- plots_pie_regionmarginal %>%
    filter(region == iregion) %>%
    group_by_at(.vars=c("sector","color_f")) %>% 
    summarize_at(.vars=c("value"),sum,na.rm=T) %>%
    ungroup %>% 
    arrange_at(.vars=c("value")) %>%
    filter(value >=0) %>%
    arrange(desc(value))%>%
    mutate(RowNum = row_number(),
           sector = ifelse(RowNum <= 4, sector, 'Remaining')) %>%
    group_by(sector) %>%
    summarise(value = sum(value)) %>%
    arrange(desc(value))%>%
    mutate(sector = as.factor(sector)) %>%
    mutate(color_f = case_when(
    sector %in% c('ATS Extreme Temperature') ~ paste0(colors_7[7],darkop),
    sector %in% c('Air Quality') ~ paste0(colors_7[6],darkop),
    sector %in% c('Labor') ~ paste0(colors_7[5],darkop),
    sector %in% c('CIL Agriculture') ~ paste0(colors_7[4],darkop),
    sector %in% c('Rail') ~ paste0(colors_7[3],darkop),
    sector %in% c('High Tide Flooding and Traffic') ~
      paste0(colors_7[2],darkop),
    sector %in% c('Roads') ~ paste0(colors_7[1],darkop),
    sector %in% c('Wildfire') ~ paste0('#c05600',darkop),
    sector %in% c('Wind Damage') ~ paste0('#446443',darkop),
    sector %in% c('Southwest Dust') ~ paste0('#936f38',darkop),
    sector %in% c('Remaining') ~ paste0('#D3D3D3',darkop)))
  
  p_temp$fraction <- p_temp$value/sum(p_temp$value)
  # Compute the cumulative percentages (top of each rectangle)
  p_temp$ymax <- cumsum(p_temp$fraction)
  # Compute the bottom of each rectangle
  p_temp$ymin <- c(0, head(p_temp$ymax, n=-1))
  # Compute label position
  p_temp$labelPosition <- (p_temp$ymax + p_temp$ymin) / 2
  # Compute a good label
  p_temp$label <- paste0(format(round(100*p_temp$fraction, 0), 
                                nsmall = 0),'%')
  label2 = paste0(format(round(100*sum(p_temp$value)/
                                 sum(plots_pie_regionmarginal$value),1),
                         nsmall=1),'%')
  

  #plot donut data  
  p <- ggplot(p_temp, aes(ymax = ymax, ymin = ymin,xmax = 4, xmin = 3, 
                          fill = reorder(sector,(value)))) +
    geom_rect() +
    geom_text(x=4.25, 
              aes(y=labelPosition,label=''),
              size=5) +
    coord_polar(theta = "y") +
    scale_fill_manual(values =rev(p_temp$color_f), 
                    guide = NULL)+
                    #guide_legend(reverse=TRUE))+#,
                    #labels=function(x) sprintf("$%1.0f", as.double(x))) +
    theme_void()+
    xlim(c(2,4))+
    labs(fill = "Top 4 Sectors",title = paste(iregion,label2))
    
  #p
  plist[[count]] <-p
  ggsave(p,filename = paste0('fa2-2_',iregion,'.tiff'),width = 5,height = 5)

}

plist

```
## Appendix Figure A4-1.  

Annual Damages Timeseries - all sectors (national total)


Plot annual impacts by sector (National Totals)
currently ordered by decreasing mean in 2300

```{r annual_bySector_2300,eval=TRUE,fig.height=12,fig.width=9,echo=FALSE}
 plots_annual_bySector <- df_fstat %>%
   #if plotting 2300 version
   filter(year <= 2300 & year > 2100) %>%
   mutate_at(.vars = c('X025','X50','mean','X975'), 
             function(x){x / 1e9 *pricelevel_2015_to_2020}) %>% # billions 2020$
   mutate(sector = sapply(sector, 
                          function(x) gsub("ATS Extreme Temperature","Temperature Related Mortality",x))) %>%
   mutate(sector = sapply(sector, 
                          function(x) gsub("High Tide Flooding and Traffic",
                                           "Transportation Impacts from High Tide Flooding",x))) %>%
   mutate(sector = sapply(sector, function(x) gsub("CIL","",x)))

#order sectors by decreasing mean in 2300  
sectors_i <- plots_annual_bySector %>% 
         filter(year ==2300) %>%
         group_by_at(.vars=c("sector")) %>% 
         summarize_at(.vars=c("mean"),sum,na.rm=T) %>%
         ungroup %>% arrange(desc(mean), sector)

### Iterate over sectors
#create plot for each sector
plots_i <- 
  sectors_i$sector %>% lapply(function(sector_j){
      df_j  <- plots_annual_bySector %>% filter(sector == sector_j)
      ### Make plot 
      ### Plot
      plot_j  <- df_j %>% ggplot() +
      ### Ribbon plot
      geom_ribbon(aes(x=year, ymin = X025, ymax = X975),
                  alpha=0.2) +
      ### Mean Line
      geom_line(aes(x=year, y=mean), 
                linetype = 2, 
                alpha=0.8) +
         ### Median Line
      geom_line(aes(x=year, y=X50), 
                linetype = 1, 
                alpha=0.8) +
      ### Scales
      ggtitle(str_wrap(sector_j,20)) +
      scale_x_continuous("Year", 
                         breaks = seq(2100, 2300, by=50)) + #2300
      scale_y_continuous("Billions",
                        #"Annual Impacts\n(Billions)",
                         labels=label_scientific(digits = 2)) + 
      scale_fill_discrete("Sector") + 

      ### Guides/Themes
      guides(fill=guide_legend(ncol=2,byrow=FALSE)) +
      theme_bw()+
      theme(legend.position = "none",
              axis.text.x = element_text(angle = 90, vjust = 0.5, 
                                         hjust=1, size = 8),
              axis.text.y = element_text(size = 8),
              plot.title  = element_text(size = 8, face = "bold"),
      strip.text  = element_text(size = 8),
      axis.title  = element_text(size = 9))
      ### Return
      return(plot_j)
    })


### Make total plot
df_j  <- plots_annual_bySector %>% 
        group_by(year) %>%
        summarize(mean = sum(mean, na.rm=T)/1e3,
                  X50 = sum(X50, na.rm = T)/1e3,
                  X025=sum(X025, na.rm=T)/1e3, 
                  X975=sum(X975, na.rm=T)/1e3) %>%
        ungroup()
      
### Plot
plot_j  <- df_j %>% 
  ggplot() +
  ### Ribbon plot
  geom_ribbon(aes(x=year, ymin = X025, ymax = X975),
                alpha=0.2) +
  ### Mean Line
  geom_line(aes(x=year, y=mean), 
                linetype = 2, 
                alpha=0.8) +
   ### Median Line
  geom_line(aes(x=year, y=X50), 
                linetype = 1, 
                alpha=0.8) +
  ### Scales
  ggtitle(str_wrap('Total',20)) +
  scale_x_continuous("Year", 
                     #breaks = seq(2020,2100, by =20)) +2300
                     breaks = seq(2100, 2300, by=50)) +
  scale_y_continuous("Trillions",
                      labels=label_scientific(digits = 2)) + 
  scale_fill_discrete("Sector") + 

### Guides/Themes
  guides(fill=guide_legend(ncol=2,byrow=FALSE)) +
  theme_bw()+
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90, vjust = 0.5, 
                                  hjust=1, size = 8),
        axis.text.y = element_text(size = 8),
        plot.title  = element_text(size = 8, face = "bold"),
        strip.text  = element_text(size = 8),
        axis.title  = element_text(size = 9))

       
### Arrange plots
### Add plots together
num_plots = length(plots_i)+1
for(j in 1:num_plots){
  if(j == 1){ plot_i <- plots_i[[j]] 
  } else if(j ==num_plots) { plot_i <- plot_i + plot_j
  } else { plot_i <- plot_i + plots_i[[j]] 
  }
}
### Layout
plot_i <- plot_i + plot_layout(ncol = 3)
plot_i <- plot_i + 
          plot_annotation(title = "Annual Climate-Driven Impacts",
                          caption = "")
  
plot_i

ggsave(plot = plot_i, filename = 'fa4-1.tiff',width = 9,height = 12)

```

##Appendix Figure A4-2 
NPD - Discounting Method Box Plot

```{r FigureA4-2, fig.height=5, fig.width=7, echo=FALSE}

## full streams
#data <- scghg_data %>%
#        mutate(adaptation = 'Default Adaptation')

data <- npd_data

##########################
######### by discount rate
##########################

## plot data specific to this plot
plot.data = data %>% 
  filter(discount.rate %in% 
           c('1.5% Ramsey', '2.0% Ramsey', '2.5% Ramsey', "3.0% Ramsey","3.0% CDR"), #2.0% CDR #Figure A6
           #c('1.5% Ramsey', '2.0% Ramsey', '2.5% Ramsey', "3.0% Ramsey"), #Figure 6
         emissions.year==2020) %>% 
  distinct() %>% 
  arrange(trial) %>% 
  ungroup()

## select grouping
group = c('emissions.year', 'gas', 'discount.rate')

## labels
plot.data %<>% group_by_at(group) %>%
  mutate(scghg.mean  = mean(scghg),
         scghg.lower = quantile(scghg,.025),
         scghg.upper = quantile(scghg,.975),
         scghg.75 = quantile(scghg,.75),
         label.position = mean(scghg)) %>%
  ungroup()


## ordering of central rate for alpha transparency
plot.data$discount.rate <- factor(plot.data$discount.rate, 
                                  levels=c("1.5% Ramsey", "2.0% Ramsey", 
                                           "2.5% Ramsey", "3.0% Ramsey",
                                           "2.0% CDR","3.0% CDR"))

## ordering of damage functions
#plot.data$adaptation <- factor(plot.data$adaptation, 
#                               levels=c('Default Adaptation'))

## all three just the boxplot
## function to help with boxplots
quantiles_95 <- function(x) {
  r <- quantile(x, probs=c(.025, 0.25, 0.5, 0.75, 0.975))
  names(r) <- c("ymin", "lower", "middle", "upper", "ymax")
  r
}

## function for labels
means = plot.data %>% 
  group_by(discount.rate) %>% 
  summarise(means=mean(scghg)) %>% 
  mutate(across(c('means'), ~ signif(.,2))) 

p <- plot.data %>%
  ggplot() +
  stat_summary(aes(x=scghg, y=discount.rate, color=discount.rate,
                   fill=discount.rate),
               alpha    = 0.5,
               geom     = "boxplot",
               fun.data = quantiles_95, 
               width    = 0.5, 
               #position = position_dodge(.9),
               show.legend=T) + 
  stat_summary(aes(x=scghg, y=discount.rate, color=discount.rate),
               alpha = 1,
               fun   = mean, 
               geom  = "point", 
               shape = 8, 
               size  = 4, 
               #position = position_dodge(.9),
               show.legend=F) +
  geom_text(data=means, 
            aes(x=means, y=discount.rate, group=discount.rate, 
                label=paste0('$', round(means, 2)), vjust=-1.5),
            position = position_dodge(1.3),
            color    = 'grey20',
            size     = 4,
            family   = "sans-serif") +
  labs(
    # title = 'XXX')),
    x     = expression(paste('Dollars per ton of ', CO[2])),
    y     = '',
    color = 'Discount Rate',
    fill  = 'Discount Rate',
    alpha = 'Discount Rate') +
  scale_x_continuous(
  #  limits = c(0,110),
  #  # breaks = seq(0,5,1), 
    labels = scales::dollar)+#,
  #  expand = expansion(mult=c(0,0))) +
  scale_y_discrete(expand = expansion(mult=c(0.0,0))) +
  scale_color_manual(values = colors_6) +
  scale_fill_manual(values  = colors_6) +
  coord_cartesian(xlim = c(0,quantile(plot.data$scghg,0.99))) + #0.985
  theme_minimal() +
  theme(legend.position = c(0.75, 0.65),
        legend.title    = element_text(size=12),
        legend.text     = element_text(size=12),
        legend.key.size = unit(0.75, 'cm'),
        legend.margin   = margin(-10, 0, 0, 0),
        axis.title.x    = element_text(size=14,hjust=0.5,vjust=-0.5),
        axis.text       = element_text(size=12),
        #axis.text.x = element_text(scales::dollar),
        axis.text.y     = element_blank(),
        plot.caption    = element_text(size=11, hjust=0.5),
        #text           = element_text(family="sans-serif", color='grey20')) +
        text            = element_text( color='grey20')) +
  guides(color = guide_legend(reverse = T),
         fill  = guide_legend(reverse = T, 
                              override.aes = list(linetype = 0, alpha=0.7)),
         alpha = guide_legend(reverse = T))#
 

p

ggsave(p, filename = 'fa4-2.tiff', width=7, height=3.5, bg = 'white')
```
